Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-06 paper.tex
Some text formatting for Table 2

\begin{table} \centering
\begin{tabular}{l|c|c|c|c|c} \hline
\multicolumn{1}{c}{} & \multicolumn{3}{c}{\textbf{Jackson et al. (2021)}} &
\multicolumn{2}{c}{\textbf{sc2ts (wide ARG)}} \\ \hline
\textbf{Sample} &
\textbf{Group} & \textbf{Parents} & \thead{Breakpoint \\
interval(s)} &
\textbf{Parents} & \thead{Breakpoint \\ interval(s)} \\
\hline ALDP-11CF93B & A
& \thead{B.1.177 \\ Alpha} & 21,255–21,613 & \thead{B.1.177.18 \\ Alpha} &
21,256–22,227 \\ ALDP-125C4D7 & A & \thead{B.1.177 \\ Alpha} & 21,255–21,613 &
\thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\ ALDP-130BB95 & A &
\thead{B.1.177 \\ Alpha} & 21,255–21,613 & \thead{B.1.177.18 \\ Alpha} &
21,256–22,227 \\ LIVE-DFCFFE & A & \thead{B.1.177 \\ Alpha} & 18,998–20,294 &
\thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\ QEUH-CCCB30 & B &
\thead{B.1.36.28 \\ Alpha} & 6,528–6,953 & \thead{B.1.36 \\ Alpha} &
6,529–6,954 \\ QEUH-CD0F1F & B & \thead{B.1.36.28 \\ Alpha} & 6,528–6,953 &
\thead{B.1.36 \\ Alpha} & 6,529–6,954 \\ MILK-1166F52 & C & \thead{Alpha \\
B.1.221.1} & 25,996–27,441 & \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
MILK-11C95A6 & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 & \thead{Alpha \\
B.1.221} & 25,997–27,972 \\ QEUH-109B25C & C & \thead{Alpha \\ B.1.221.1} &
25,996–27,441 & \thead{Alpha \\ B.1.221} & 25,997–27,972 \\ MILK-126FE1F & D &
\thead{B.1.36.39 \\ Alpha} & 20,703–23,062 & \thead{B.1.36.39 \\ Alpha} &
22,445–23,063 \\ RAND-12671E1 & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062
& \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\ RAND-128FA33 & D &
\thead{B.1.36.39 \\ Alpha} & 20,703–23,062 & \thead{B.1.36.39 \\ Alpha} &
22,445–23,063 \\ CAMC-CBA018 & n/a & \thead{B.1.177 \\ Alpha} & 20,389–21,254 &
\thead{B.1.177 \\ Alpha} & 16,177–21,255 \\ CAMC-CB7AB3 & n/a & \thead{Alpha \\
B.1.177 \\ Alpha} & \thead{3,267–4,474 \\ 20,389–21,254} & \thead{Alpha \\
B.1.177 \\ Alpha} & \thead{3,268–5,388 \\ 16,177–21,255} \\ MILK-103C712 & n/a
& \thead{B.1.177.17 \\ Alpha} & \thead{408–444 \\ 26,801–27,876} & n/a & n/a \\
QEUH-1067DEF & n/a & \thead{Alpha \\ B.1.177.9} & 10,523–10,869 & \thead{Alpha
\\ B.1.177} & 7,729–10,870 \\ \hline
\end{tabular}
\caption{\label{tab:jackson}Recombinant sequences involving the Alpha (B.1.1.7)
variant reported by \cite{Jackson2021-ik} have recombinant
ancestry in the wide ARG. The breakpoint intervals and Pango lineage
assignments of the parents were taken from Table 2 (3SEQ results) of Jackson et
al., except the Pango lineage assignment of the parents of group B
recombinants, which were taken from Table 1 (motif-based results).}
\end{table}

>>>>

% FIXME there's too much vspace between the rows here. Probably best to redo
% the formatting.
\begin{table} \centering
\begin{tabular}{l|c|c|c|c|c} \hline
\multicolumn{1}{c}{} & \multicolumn{3}{c}{\textbf{Jackson et al. (2021)}} &
\multicolumn{2}{c}{\textbf{sc2ts (wide ARG)}} \\ \hline
\textbf{Sample} &
\textbf{Group} & \textbf{Parents} & \thead{Breakpoint \\
interval(s)} &
\textbf{Parents} & \thead{Breakpoint \\ interval(s)} \\
\hline ALDP-11CF93B & A
    & \thead{B.1.177 \\ Alpha} & 21,255–21,613 & \thead{B.1.177.18 \\ Alpha} &
21,256–22,227 \\
    ALDP-125C4D7 & A & \thead{B.1.177 \\ Alpha} & 21,255–21,613 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
ALDP-130BB95 & A & \thead{B.1.177 \\ Alpha} & 21,255–21,613 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
LIVE-DFCFFE & A & \thead{B.1.177 \\ Alpha} & 18,998–20,294 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
QEUH-CCCB30 & B & \thead{B.1.36.28 \\ Alpha} & 6,528–6,953 &
    \thead{B.1.36 \\ Alpha} & 6,529–6,954 \\
QEUH-CD0F1F & B & \thead{B.1.36.28 \\ Alpha} & 6,528–6,953 &
    \thead{B.1.36 \\ Alpha} & 6,529–6,954 \\
MILK-1166F52 & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
MILK-11C95A6 & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
QEUH-109B25C & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
MILK-126FE1F & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
RAND-12671E1 & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
RAND-128FA33 & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
CAMC-CBA018 & n/a & \thead{B.1.177 \\ Alpha} & 20,389–21,254 &
    \thead{B.1.177 \\ Alpha} & 16,177–21,255 \\
CAMC-CB7AB3 & n/a & \thead{Alpha \\ B.1.177 \\ Alpha} & \thead{3,267–4,474 \\ 20,389–21,254} &
     \thead{Alpha \\ B.1.177 \\ Alpha} & \thead{3,268–5,388 \\ 16,177–21,255} \\
MILK-103C712 & n/a & \thead{B.1.177.17 \\ Alpha} & \thead{408–444 \\ 26,801–27,876} &
    n/a & n/a \\
QEUH-1067DEF & n/a & \thead{Alpha \\ B.1.177.9} & 10,523–10,869 &
    \thead{Alpha \\ B.1.177} & 7,729–10,870 \\ \hline
\end{tabular}
\caption{\label{tab:jackson}Recombinant sequences involving the Alpha (B.1.1.7)
variant reported by \cite{Jackson2021-ik} have recombinant
ancestry in the wide ARG. The breakpoint intervals and Pango lineage
assignments of the parents were taken from Table 2 (3SEQ results) of Jackson et
al., except the Pango lineage assignment of the parents of group B
recombinants, which were taken from Table 1 (motif-based results).}
\end{table}
